\thesistitle

### 2019-07-30 sections/clonerefactor.tex
Is not a partial method

\subsection{Contents}\label{sec:setupcontents}
Finally, we looked at what nodes individual clone instances span. We selected a set of catagories on the basis of empirical evaluation of a set of clones in our dataset. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method. The declaration itself is not included.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

@@

Because of this, we defined a set of categories of things that can obstruct a refactoring opportunity using the ``Extract Method'' technique. We defined the following categories:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of the previous section, the ``extract method'' refactoring technique cannot be applied.
    \item \textbf{Top-level Node Is Not A Statement}: The topmost node of a clone instance is not a statement.
    \item \textbf{Overlaps}: There is overlap within the clone class.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}

@@

>>>>

\subsection{Contents}\label{sec:setupcontents}
Finally, we looked at what nodes individual clone instances span. We selected a set of catagories on the basis of empirical evaluation of a set of clones in our dataset. We selected the following categories to be relevant for refactoring:
\begin{enumerate}
  \item \textbf{Full Method/Constructor/Class/Interface/Enumeration:} A clone that spans a full class, method, constructor, interface or enumeration, including its declaration.
  \item \textbf{Partial Method/Constructor:} A clone that spans (a part of) the body of a method/constructor. The declaration itself is not included.
  \item \textbf{Several Methods:} A clone that spans over two or more methods, either fully or partially, but does not span anything but methods (so not fields or anything in between).
  \item \textbf{Only Fields:} A clone that spans only global variables.
  \item \textbf{Other:} Anything that does not match with above-stated categories.
\end{enumerate}

@@

Because of this, we defined a set of categories of things that can obstruct a refactoring opportunity using the ``Extract Method'' technique. We defined the following categories:
\begin{itemize}
    \item \textbf{Complex Control Flow}: This clone contains \texttt{break}, \texttt{continue} or \texttt{return} statements, obstructing the possibility of method extraction.
    \item \textbf{Spans Part Of A Block}: This clone spans a part of a statement.
    \item \textbf{Is Not A Partial Method}: If the clone does not fall in the ``Partial method'' category of section \ref{sec:setupcontents}, the ``extract method'' refactoring technique cannot be applied.
    \item \textbf{Top-level Node Is Not A Statement}: The topmost node of a clone instance is not a statement.
    \item \textbf{Overlaps}: There is overlap within the clone class.
    \item \textbf{Can Be Extracted}: This clone is a fragment of code that can directly be extracted to a new method. Then, based on the relation between the clone instances, further refactoring techniques can be used to refactor the extracted methods (for instance ``pull up method'' for clones in sibling classes).
\end{itemize}

@@

\subsubsection{Is Not A Partial Method}
The ``Extract Method'' refactoring can only refactor code in the body of a method. We mapped the contents of clones in section \ref{sec:setuplocation}. Here we defined the ``Partial Method'' catagory as \textit{a clone that spans (a part of) the body of a method. The declaration itself is not included.} If the clone does not fall within this category, ``Extract Method'' is probably not the correct technique for refactoring such clones.
